\vspec{} and Friends: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-07-30 src/tex/ms.tex
Remove MIRECLE example

\subsection{MIRECLE Phase Curve}
In this example we will look at the best-case target for the Mid-IR Exoplanet CLimate Explorer \citep[MIRECLE,][]{mandell2022}
mission concept: Proxima Centauri b with no stellar variability. We will instead examine the expected noise produced by this observation
and assess the detectability of the planet in a single orbit. \vspec{} uses the noise models built into PSG, allowing native support for
noise due to the instrument, source, and astrophysical background.

We use \vspec{}'s built-in MIRECLE instrument template, which includes a 2 m aperture and observes from 1-18 $\mu m$ with $R=50$.
We draw stellar and bulk planetary parameters from the NExScI Exoplanet Archive\footnote{\url{https://exoplanetarchive.ipac.caltech.edu/overview/proxima\%20cen}}
and assume $i=85^\circ$ and Earth density. The GCM we use has a Bond albedo of 0.3, $\epsilon=1.5$, $P_{\rm surf} = 1 \text{bar}$ and a 100 ppm \ce{CO2} atmosphere with a \ce{N2} background.
We ran the simulation for one orbit with an 24 hour cadence. Because this is a best-case scenario, we assumed perfect knowledge of the stellar spectrum.
We are left with the planetary spectrum and photon noise from the star.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/mirecle.pdf}
    \caption{
        Simulated spectra of Proxima Centauri b observed by MIRECLE. Noise and error bars based on 24 hour integrations with a 2 m aperture MIRECLE
        space telescope.
        }
    \script{mirecle.py}
    \label{fig:mirecle}
\end{figure}

>>>>

% \subsection{MIRECLE Phase Curve}
% In this example we will look at the best-case target for the Mid-IR Exoplanet CLimate Explorer \citep[MIRECLE,][]{mandell2022}
% mission concept: Proxima Centauri b with no stellar variability. We will instead examine the expected noise produced by this observation
% and assess the detectability of the planet in a single orbit. \vspec{} uses the noise models built into PSG, allowing native support for
% noise due to the instrument, source, and astrophysical background.

% We use \vspec{}'s built-in MIRECLE instrument template, which includes a 2 m aperture and observes from 1-18 $\mu m$ with $R=50$.
% We draw stellar and bulk planetary parameters from the NExScI Exoplanet Archive\footnote{\url{https://exoplanetarchive.ipac.caltech.edu/overview/proxima\%20cen}}
% and assume $i=85^\circ$ and Earth density. The GCM we use has a Bond albedo of 0.3, $\epsilon=1.5$, $P_{\rm surf} = 1 \text{bar}$ and a 100 ppm \ce{CO2} atmosphere with a \ce{N2} background.
% We ran the simulation for one orbit with an 24 hour cadence. Because this is a best-case scenario, we assumed perfect knowledge of the stellar spectrum.
% We are left with the planetary spectrum and photon noise from the star.

% \begin{figure}
%     \centering
%     \includegraphics[width=0.5\textwidth]{figures/mirecle.pdf}
%     \caption{
%         Simulated spectra of Proxima Centauri b observed by MIRECLE. Noise and error bars based on 24 hour integrations with a 2 m aperture MIRECLE
%         space telescope.
%         }
%     \script{mirecle.py}
%     \label{fig:mirecle}
% \end{figure}
